I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-04-22 lipics-master/relatedwork.tex
update MN-BAB in introduction

>>>>

{\color{red} MN-BaB \cite{ferrari2022complete} is another state-of-the-art verifier which is a development of PRIMA. As shown in its name, it uses a combination technique of multi-neuron constraints and Branch and Bound. According to their experiments results, MN-BaB has a similar speed and accuracy as $\alpha$,$\beta$ CROWN. So we do not compare our experiments results to MN-BaB separately.}
